SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-04 docs/questioning.tex
some work on analysis - testing

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references:
locus {\sc x}~\cite{KKVJ06,KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,MKS09,HO05,HO06,HO05b,SMS13},
locus $\Omega$~\cite{BK04,LLW02}.}
\end{figure*}

@@

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e. {\sc sql}
or {\sc xp}ath queries) in various forms, and detect attacks
as outliers from the set of valid code statements.
An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
{\sc sql} injection (locus $\Omega$) attacks by recording all database transactions.
Subsequent refinements by Valeur et al.~\cite{VMV05}
tagged each transaction with the corresponding application
as an extension of their anomaly detection framework called
{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09} is
a signature-based mechanism that prevents {\sc sql} and
{\sc xp}ath injection attacks. The signatures generated
during a training phase, are based on features that can
depend either on the code statement or on its execution
environment (i.e. the stack trace).
Then, at runtime, the mechanism checks all statements for compliance
and can block code statements containing injected elements (locus {\sc z}).
Furthermore, {\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool
that also detects {\sc sql} injection attacks (locus {\sc z})
by associating a query model with the location of every
{\sc sql} statement within the application.
Then at runtime, monitors the application's execution to
detect when {\sc sql} statements diverge from the expected model.

@@

>>>>

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.61]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references:
locus {\sc x}~\cite{KJKV09,TNH07,NSS06,APKLM10,APKLM10,SPPGMMB04,ML10,YCIS07,PSC09,VDDPJ11,OWVS08,DDHPJ10,GC09,APKLM10,VFJKKV07,SLMS14},
locus {\sc y}~\cite{RDWDE07,JKK06a,JB07,NLC07,WPLKK09,JEP08},
locus {\sc z}~\cite{BWS05,SW06,PS11,HCF05,XBS06,PB05,PMP11,MS09,HO05,HO06,HO05b,SMS13},
locus $\Omega$~\cite{BK04,LLW02}.}
\end{figure*}

@@

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e. {\sc sql}
or {\sc xp}ath queries) in various forms, and detect attacks
as outliers from the set of valid code statements.
An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
{\sc sql} injection (locus $\Omega$) attacks by recording all database transactions.
Subsequent refinements by Valeur et al.~\cite{VMV05}
tagged each transaction with the corresponding application
as an extension of their anomaly detection framework called
{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09,MKLS11} is
a signature-based mechanism that prevents {\sc sql} and
{\sc xp}ath injection attacks. The signatures generated
during a training phase, are based on features that can
depend either on the code statement or on its execution
environment (i.e. the stack trace).
Then, at runtime, the mechanism checks all statements for compliance
and can block code statements containing injected elements (locus {\sc z}).
Furthermore, {\sc amnesia}~\cite{HO05,HO06,HO05b} is a tool
that also detects {\sc sql} injection attacks (locus {\sc z})
by associating a query model with the location of every
{\sc sql} statement within the application.
Then at runtime, monitors the application's execution to
detect when {\sc sql} statements diverge from the expected model.

@@

\subsection{Testing}

\begin{figure}
\begin{center}
\leavevmode
\includegraphics[scale=0.47]{defect-percentages.png}
\end{center}
\caption{\label{fig:defect_sources}A pie showing where the
authors reffered to, to find vulnerabilities to test
their mechanims. We also provide which source was used
by which publication:
{\it Bugtraq}~\cite{PB05,KKVJ06,KJKV09,JEP08},
{\sc cve}~\cite{XBS06,NLC07,VFJKKV07,PMP11,BK04,JB07,SMS13,WPLKK09},
{\sc xss}ed.com~\cite{NSS06,APKLM10},
ha.ckers.org~\cite{TNH07,PSC09,LV09},
Microsoft~\cite{RDWDE07}.}
\end{figure}

Table~\ref{tab:comp} indicates that 27 out of
34 mechanisms were tested on real-world applications
known to be vulnerable. The vulnerabilities
associated with these applications are enlisted
in the following providers: the Common Vulnerabilities
and Exposures ({\sc cve})
database,\footnote{\url{https://cve.mitre.org/}}
the {\it Bugtraq}\footnote{\url{http://seclists.org/bugtraq/}}
security mailing list, the
{\sc xss}ed.com\footnote{\url{www.xssed.com}}
security bulletin provider, Microsoft's security
bulletin\footnote{\url{https://technet.microsoft.com/en-us/security/bulletin}}
and the ha.ckers.org\footnote{\url{www.xssed.com}}
security bulletin provider. Figure~\ref{fig:defect_sources}
presents how many (in terms of percentages) and which
(in the figure's caption) authors referred to which source.
In numerous occassions authors performed tests based
on the same applications. For instance, 12 mechanisms
were tested on a vulnerable version of
{\sc phpbb}.\footnote{https://www.phpbb.com/}

\subsection{Trade-offs}

\subsection{Designing New Mechanisms}
